---
title: "Assignment 1"
author: "Harish Kumar Uddandi"
date: "2022-10-01"
output:
  word_document: default
  html_document: default
  pdf_document:  default
---

##installed a ISLR Package
##created a new R-notebook file

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


##calling the ISLR library 

```{r}
library(ISLR)
Carseats_p1<-Carseats
```


##print and summary of cardataseats
```{r}
summary(Carseats_p1)
print(Carseats_p1)
nrow(Carseats_p1) # the observations(rows) this dataset contains  



```

How many observations (rows) this dataset contains? = 400

##maximum value of advertising attribute

```{r}
max(Carseats_p1$Advertising)

```


##IQR of Price attribute

```{r}

IQR(Carseats_p1$Price)

```
##scatter plot between sales and price

```{r}
plot(Carseats_p1$Sales,Carseats_p1$Price,main = "scatter plot between sales and price",xlab = "sales",ylab = "Price")

```

##barplot between sales and price

```{r}
barplot(Carseats_p1$Sales,Carseats_p1$Price)

```


## scatter plot between sales and prices by  using abline

```{r}
plot(Carseats_p1$Sales, Carseats_p1$Price, main = "Scatterplot between Price and Sales", xlab = "Sales", ylab = "Price",abline(Carseats_p1$Sales,Carseats_p1$Price))

```

##correlation between sales and price

```{r}
cor(Carseats_p1$Sales,Carseats_p1$Price)

```



